\section{Suggested team} \label{sec:team}

In \secref{sec:items} some \gls{software} products are listed which a team could potentially look after.
These are all summit support items which are used and needed for operations.
They are a mixture of front and back end capabilities and would require interaction with TSSW and \gls{DM}.
So this team would be a DevOps type team with full \gls{stack} capability and skills to debug all levels on the summit.

There are a few people in T\&S already working in the or related areas, such as Rob, Michael, Sebastian, Tiago and Merlin.
However all have other roles/jobs so we believe there is a shortage of at least one full \gls{stack} engineer and more likely two in this area.


If this \gls{software} is to be supported on call and 24/7 the team would need to be much larger.


\subsection{Where would the team sit}
TSSW is the closest to this topic so it should be a group in TSSW under Andy Clements.
Michael Reuter would make a good team lead for this - provided we give him the required resources.
Tiago Ribeiro would be an obvious product owner - even if he is quite involved.
This is completely analogs to similar setups within DM Pipelines.

It is not clear if there is an equivalent \gls{NOIRLab} structure for summit support \gls{software} which
a mixture between Science processing, \gls{QA} tools, \gls{monitoring} and control software.

\subsection{Overall software management}
A further topic for discussion is the overall coordination of software in \VRO  \gls{Operations} - a role not currently in the operations plan and for which an Joint \gls{Operations} \gls{Review} recommendation remains pending\jira{PREOPS-3521}.

In construction William O'Mullane has the role of deputy Project manager for software.  This may be  crisply defined as being responsible for all IT and Software on the project.
The construction role is outlined in  \secref{sec:deputypm}.
A potential role in operations is discussed in \secref{sec:opssw}


\subsubsection{Construction - Deputy PM-Software \& IT} \label{sec:seputypm}
\citeds{Document-25351} defines this as follows:

\begin{itemize}
\item Roles
\begin{itemize}
\item Facilitate all software decision making across the project.
\item Facilitate all IT decisions across the project.
\item Manager of managers for software and IT roles – even if such managers are in different
subsystems.
\item Mentor senior IT and Software personnel.
\end{itemize}
Responsibilities
\begin{itemize}
\item Though a large fraction of software on the project is in Data Management there is also
significant software in Telescope \& Site and Camera. The project manager delegates
responsibility Deputy PM is responsible for the smooth running of software in all
subsystems.
\item Ultimately, the DMPM, in conjunction with his/her peer Project Managers (Telescope,
Camera), is responsible for delivering an integrated Rubin system.
\item The Deputy Project Manager has the responsibility for resolving conflicts involving IT
and Software between IT, T\&S, Camera and DM.
Leadership Roles, Responsibilities, Authorities, Accountabilities (R2A2s) | Document-25351 (2.0) | Latest Revision Date 2022-04-07
22
\item The Deputy PM as a manager of mangers is responsible for obtaining and maintaining
managers in senior software management roles. Specifically head of Telescope and
Site Software, IT Chile IT Tucson and Data Management.
\item Assist software managers in definition of scope, funding requests, risk management
and mitigation.
\item Ensure compatible and where possible similar work and management practices for
software across subsystems.
\item Assist with reviews and review preparations from a software perspective.
\item Provide leadership to senior managers involved in IT and Software across Rubin.
\item Foster a good, equitable, diverse and inclusive working environment within Rubin.
\end{itemize}
\item Authorities
\begin{itemize}
\item  In the absence of the PM the deputy carries full authority and decision making powers
of the PM.
\item Approve or execute as appropriate all Software/IT outsourcing contracts.
\item Approve or execute as appropriate all IT equipment and licensing purchases.
\end{itemize}
\item Accountabilities
\begin{itemize}
\item Budgeting of software and IT across Rubin should be monitored.
\item Decisions made on software and IT especially across subsystem boundaries.
\item Actions and decisions of senior software and IT managers across Rubin Specifically head of Telescope and Site Software, IT Chile IT Tucson and Data Management.

\end{itemize}
\end{itemize}


\subsubsection{Operations Software} \label{sec:opssw}

In Rubin Operations there is no head of software


